Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-09-28 manuscript.Rmd
Added exeperiment 1 results write up

# Results
## Experiment 1
The results from the first experiment are shown in figure \@ref(fig:pupildata) and figure \@ref(fig:EEGdata). Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
```{r include=FALSE, results='hide'}

>>>>

# Results
## Experiment 1
The results from the first experiment are shown in figure \@ref(fig:pupildata) and figure \@ref(fig:EEGdata). Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).

Figure \@ref(fig:pupildata) is showing the results for the pupillometry. Figure \@ref(fig:pupildata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:pupildata)b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli. Figures \@ref(fig:pupildata)c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz. In the same-frequency condition at 2 Hz (fig. \@ref(fig:pupildata)c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration. In the cross-frequency condtion at 2 Hz (fig. \@ref(fig:pupildata)d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition. Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig. \@ref(fig:pupildata)e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels. This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils. Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.

Figure \@ref(fig:EEGdata) shows the results for EEG. Figure \@ref(fig:EEGdata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:EEGdata)b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \@ref(fig:EEGdata)c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \@ref(fig:EEGdata)f-h show the CRFs at the second harmonic. What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig. \@ref(fig:EEGdata)c) and second (fig. \@ref(fig:EEGdata)f) harmonic are showing very high summation of binocular signals. The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses. This is especially clear at the highest contrasts. For the cross-frequency condition at 2 Hz and 4 Hz (fig. \@ref(fig:EEGdata)d and \@ref(fig:EEGdata)g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig. \@ref(fig:EEGdata)e) and 3.2 Hz (fig. \@ref(fig:EEGdata)h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a  linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex. 
```{r include=FALSE, results='hide'}

### 2022-09-28 manuscript.tex
Added exeperiment 1 results write up

>>>>

Figure \ref{fig:pupildata} is showing the results for the pupillometry. Figure \ref{fig:pupildata}a is showing the group average waveform for binocular presentation. Figure \ref{fig:pupildata}b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli. Figures \ref{fig:pupildata}c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz. In the same-frequency condition at 2 Hz (fig.~\ref{fig:pupildata}c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration. In the cross-frequency condtion at 2 Hz (fig.~\ref{fig:pupildata}d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition. Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.~\ref{fig:pupildata}e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels. This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils. Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.

Figure \ref{fig:EEGdata} shows the results for EEG. Figure \ref{fig:EEGdata}a is showing the group average waveform for binocular presentation. Figure \ref{fig:EEGdata}b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \ref{fig:EEGdata}c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \ref{fig:EEGdata}f-h show the CRFs at the second harmonic. What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.~\ref{fig:EEGdata}c) and second (fig.~\ref{fig:EEGdata}f) harmonic are showing very high summation of binocular signals. The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses. This is especially clear at the highest contrasts. For the cross-frequency condition at 2 Hz and 4 Hz (fig.~\ref{fig:EEGdata}d and \ref{fig:EEGdata}g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig.~\ref{fig:EEGdata}e) and 3.2 Hz (fig.~\ref{fig:EEGdata}h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.
